Analysis for Project

### 2021-10-11 analysis/analysis.Rmd
Maintain 80 character limit in analysis.Rmd
Add plot showing difference from midpoint expectation

>>>>

```{r}
#make a plot showing difference from middle expectation by model
coef_table <- bind_rows(tidy(model1) %>%
                          filter(str_detect(term, "race") & 
                                   str_detect(term, "/") & 
                                   !str_detect(term, "Multiracial")) %>%
                          mutate(model="model1"),
                        tidy(model4) %>%
                          filter(str_detect(term, "race") & 
                                   str_detect(term, "/") & 
                                   !str_detect(term, "Multiracial")) %>%
                          mutate(model="model4"))
ggplot(coef_table, aes(x=reorder(term, estimate, mean), y=estimate, color=model, group=model))+
  geom_point(position="dodge")+
  coord_flip()
```
